Impact of Satellite Constellations on the Legacy Survey of Space and Time

### 2022-10-05 ms.tex
Updates from Overleaf

\end{abstract}

@@

\begin{figure}
    \centering
    \plottwo{plots/temp}{}
    \caption{Caption}
    \label{fig:twi_neo}
\end{figure}

>>>>

XXX--bottom line. Even in the case of multiple megaconstellations ion orbit, we expect Rubin would only lose $\sim$0.02\% of science pixels to streaks. Given reasonable predicitons of satellite orbits we find we can reduce losses by a factor of 2 with minimal impact to the survey science goals. Twilight observations at high airmass with no scheduling mitigation could see pixel losses up to 0.06\%. 
\end{abstract}

@@

\begin{figure}
    \centering
    \plottwo{plots/temp/opsim_Count_night_night_lt_366_and_visitExposureTime_lt_20_HEAL_SkyMap.pdf}{plots/twilight_curves.pdf}
    \caption{Impact of streaks on twilight NEO observations that can not easily be shifted to dodge satellites.}
    \label{fig:twi_neo}
\end{figure}
